16s lefse

### 2021-03-25 scripts/43_comparisons_3.Rmd
update

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  mutate(clado_cmd = str_glue('plot_cladogram.py {fns}.res {fns}_clado.pdf  --label_font_size 4 --dpi 300 --format pdf --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd_taxa.sh', col_names = F)
```

>>>>

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.pdf --format pdf --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  mutate(clado_cmd = str_glue('plot_cladogram.py {fns}.res {fns}_clado.pdf  --label_font_size 4 --dpi 300 --format pdf --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd_taxa.sh', col_names = F)
```

### 2021-03-25 scripts/56_rethinking_genera.Rmd
update

@@

```{r}
# plot them together in one 
bind_rows(
  res_top %>% mutate(grp = 'top'),
  res_bot %>% mutate(grp = 'bot')
) %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white', add = 'mean',
                  xlab = 'Predicted probability of CR d100', ylab = 'Probability density')

>>>>

```{r}
post <- extract.samples(gtox) 
meta_ <- meta %>% 
  select(Akkermansia:Ruminococcus)

N <- 100
# for the top and bottom quantile range of Bacteroides relab
ba_top <- meta_ %>% 
  filter(Bacteroides >= quantile(meta$Bacteroides, 0.9))
ba_bot <- meta_ %>% 
  filter(Bacteroides <= quantile(meta$Bacteroides, 0.1))

# for the top quantile patients 
res_top <- pmap(ba_top, function(Akkermansia, Bacteroides, Enterococcus, Faecalibacterium, Ruminococcus){
  per_pt_sample_post_prob(Akkermansia, Bacteroides, Enterococcus, Faecalibacterium, Ruminococcus)
}) %>% 
  set_names(paste('P', seq(1, nrow(ba_top)), sep = '')) %>% 
  bind_rows(.id = 'pt')

# for the bottom quantile patients  
res_bot <- pmap(ba_bot, function(Akkermansia, Bacteroides, Enterococcus, Faecalibacterium, Ruminococcus){
  per_pt_sample_post_prob(Akkermansia, Bacteroides, Enterococcus, Faecalibacterium, Ruminococcus)
}) %>% 
  set_names(paste('P', seq(1, nrow(ba_bot)), sep = '')) %>% 
  bind_rows(.id = 'pt')

# plot them together in one 
bind_rows(
  res_top %>% mutate(grp = 'top'),
  res_bot %>% mutate(grp = 'bot')
) %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white', add = 'mean',
                  xlab = 'Predicted probability of Toxicity', ylab = 'Probability density') +
  ggsave('../figs/predicted_tox_bacteroides_top_bottom_10.pdf', width = 7, height = 5)
```

@@

```{r}
# plot them together in one 
bind_rows(
  res_top %>% mutate(grp = 'top'),
  res_bot %>% mutate(grp = 'bot')
) %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white', add = 'mean',
                  xlab = 'Predicted probability of CR d100', ylab = 'Probability density')+
  ggsave('../figs/predicted_CR_Ruminococcus_top_bottom_10.pdf', width = 7, height = 5)

### 2021-03-25 scripts/57_16s_lefse.Rmd
update

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1  -u 2 -o 1000000   ')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  mutate(clado_cmd = str_glue('plot_cladogram.py {fns}.res {fns}_clado.pdf  --label_font_size 4 --dpi 300 --format pdf --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/amplicon/lefse/lefse_run_cmd_taxa.sh', col_names = F)

>>>>

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1  -u 2 -o 1000000   ')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.pdf --format pdf  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  mutate(clado_cmd = str_glue('plot_cladogram.py {fns}.res {fns}_clado.pdf  --label_font_size 4 --dpi 300 --format pdf --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/amplicon/lefse/lefse_run_cmd_taxa.sh', col_names = F)
